Titeln på avhandlingens språk

### 2022-08-25 model.tex
explaining ttf

Take \( \{ t_0, t_1, \ldots, t_{n + 1} \} \) a series of discrete and sequential sampling intervals at which the \ac{WCA} captures the state of the physical system --- see \cref{fig:step}.
\( t_0 \) corresponds to the instant at which the instruction for step \( M \) is provided and the first sample for said step is taken, and \( t_{n+1} \) to the instant at which the instruction for step \( M + 1 \) is provided.
Furthermore, \( t_c \) represents the instant at which the user finishes performing the instruction for step \( M \); the interval \( t_c - t_0 \) we call the \emph{execution time} of \( M \).
From the discrete sampling nature of the \ac{WCA} application, it follows that \( t_{n - 1} \leq t_c \leq t_{n} \); in plain English, the final state of the step is --- by definition --- always reached \emph{before} the final sample of the step is taken but after the next-to-last sampling instant.
We define the intervals \( t_n - t_c \) and \( t_{n + 1} - t_n \) as the \emph{wait time} and \emph{last sample \ac{RTT}}, respectively, for step \( M \).
The sum of these two values (i.e. the interval \( t_{n + 1} - t_c \)) we call \emph{time-to-feedback}.

\emph{Execution time} and \emph{time-to-feedback} correspond to the two key metrics necessary to characterize the interactions between human behavior and system responsiveness.

\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{figs/task.png}
        \caption{%
            Overview of a task in a \ac{WCA}, composed of a series of steps.
            Each steps starts with an instruction being provided to the user and ends with the instruction for the next step.
            The \ac{WCA} continuously samples the task state, automatically triggering transitions between steps as correct (or incorrect) states are recognized.
        }\label{fig:task}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{figs/step_time.png}
        \caption{%
            Breakdown of a step into its timing components.
            The instruction for step \( M \) and \( M + 1 \) are provided to the user at \( t_0 \) and \( t_{n+1} \), respectively.
            \( t_k | k \in \{1, \ldots, n \} \) correspond to the \ac{WCA} sampling instants for step \( M \), and \( t_c \) marks the instant at which the user finishes performing the instruction.
        }\label{fig:step}
    \end{subfigure}
    \caption{}
\end{figure}

>>>>

Take \( \{ t_0, t_1, \ldots, t_{n + 1} \} \) a series of discrete and sequential sampling intervals at which the \ac{WCA} captures the state of the physical system --- see \cref{fig:step}.
\( t_0 \) corresponds to the instant at which the instruction for step \( M \) is provided and the first sample for said step is taken, and \( t_{n+1} \) to the instant at which the instruction for step \( M + 1 \) is provided.
Furthermore, \( t_c \) represents the instant at which the user finishes performing the instruction for step \( M \); the interval \( t_c - t_0 \) we call the \emph{execution time} of \( M \).
From the discrete sampling nature of the \ac{WCA} application, it follows that

\begin{equation}\label{eq:tc}
    t_{n - 1} \leq t_c \leq t_{n}
\end{equation}

In plain English, the final state of the step is --- by definition --- always reached \emph{before} the final sample of the step is taken but after the next-to-last sampling instant.
We define the intervals \( t_n - t_c \) and \( t_{n + 1} - t_n \) as the \emph{wait time} and \emph{last sample \ac{RTT}}, respectively, for step \( M \).
The sum of these two values (i.e. the interval \( t_{n + 1} - t_c \)) we call \emph{time-to-feedback}.

In~\cite{olguinmunoz:impact2021} we used \emph{delay} and \emph{execution time} as our key variables of interest.
\emph{Delay} corresponded to a set time duration the processing of each frame was padded to --- i.e. if during a series of steps delay was set to \( X \) seconds, the feedback for each frame was provided to the user at exactly \( X \) seconds after frame capture.
The correlation between delay and execution time was then studied.
Delay, however, was merely an experimental tool, and in the present paper we argue that the underlying metric driving the human behavior is rather \emph{time-to-feedback}.
If we consider that
\begin{enumerate*}[itemjoin={{; }}, itemjoin={{; and }}]
    \item \( t_c \) is uniformly distributed in the interval \( [t_{n - 1}, t_{n}] \) (see \cref{eq:tc} above and~\cite{olguinmunoz:impact2021})
    \item for a step subject to \emph{delay} \( X \), \( t_k - t_{k - 1} = X \) for all \( k \in \{1, 2, \ldots, n\} \)
\end{enumerate*},
then it must follow that, \emph{on average}, for all steps subject to a \emph{delay} \( X \):

\begin{equation}\label{eq:ttf}
    \text{\emph{time-to-feedback}} = \frac{3}{2}X
\end{equation}

Ergo, we can directly re-parameterize the data from~\cite{olguinmunoz:impact2021} to use time-to-feedback instead of delay by simply multiplying the delay value of each step by \( 1.5 \).

\newpage
\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{figs/task.png}
        \caption{%
            Overview of a task in a \ac{WCA}, composed of a series of steps.
            Each steps starts with an instruction being provided to the user and ends with the instruction for the next step.
            The \ac{WCA} continuously samples the task state, automatically triggering transitions between steps as correct (or incorrect) states are recognized.
        }\label{fig:task}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{figs/step_time.png}
        \caption{%
            Breakdown of a step into its timing components.
            The instruction for step \( M \) and \( M + 1 \) are provided to the user at \( t_0 \) and \( t_{n+1} \), respectively.
            \( t_k | k \in \{1, \ldots, n \} \) correspond to the \ac{WCA} sampling instants for step \( M \), and \( t_c \) marks the instant at which the user finishes performing the instruction.
        }\label{fig:step}
    \end{subfigure}
    \caption{}
\end{figure}
